### 2017-10-16 mcmc.tex
closing #29

In many problems that have large numbers of parameters,
  the parameters---the components or entries of the
  blob $\pars$---are not equivalent at all.
Some are global parameters, which touch or have an effect on every
sub-part of the data blob $\data$, while others are local parameteres,
which only touch a small subset of the data.
Or, in another use case, some parameters are linear parameters
that---at fixed values of the other parameters---will have a Gaussian
likelihood or posterior pdf.
In these problems, there are some directions in parameter space that
are hard to move in (they require complete re-calculation of the full
non-linear function $f(\pars)$, and other directions that are very
easy to move in (they require only partial re-calculations or the
sampling could even be analytic and exact).
For problems with these structures, Gibbs samplers are ideal, and
there are good implementations.\note{For example, \project{STAN} and \project{JAGS}; find them on the internets. DFM INSERT URLs AND REFERENCES.}

>>>>

In many problems that have large numbers of parameters,
  the parameters---the components or entries of the
  blob $\pars$---are not equivalent at all.
Some are global parameters, which touch or have an effect on every
sub-part of the data blob $\data$, while others are local parameteres,
which only touch a small subset of the data.
Or, in another use case, some parameters are linear parameters
that---at fixed values of the other parameters---will have a Gaussian
likelihood or posterior pdf.
In these problems, there are some directions in parameter space that
are hard to move in (they require complete re-calculation of the full
non-linear function $f(\pars)$, and other directions that are very
easy to move in (they require only partial re-calculations or the
sampling could even be analytic and exact).
For problems with these structures, Gibbs samplers are ideal, and
there are good implementations.\note{For example, \project{Stan}
(\url{http://mc-stan.org}).}
